%-------------------------
% Resume in Latex
% Author : Shubhro Sinha
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%\definecolor{violet}{HTML}{BF0A30}
%\definecolor{violet}{HTML}{CD143C}
%\definecolor {teal}{HTML}{ED3929}
\definecolor{GRAY}{HTML}{828282}
\definecolor{DOCOLOR}{HTML}{14145c}
%\color{DOCOLOR}
\color{black}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/shubhrosinha/}{\Large {\textcolor{teal}{Shubhro Sinha}}}} & Email : \href{mailto:shubhro22@gmail.com}{shubhro22@gmail.com}\\
  \href{https://www.linkedin.com/in/shubhrosinha/}{linkedin.com/in/shubhrosinha} &
  Mobile1 : +91-9986619004\\
  Bengaluru, Karnataka & Mobile2 : +91-8217460442
\end{tabular*}

%-----------SUMMARY-----------------
\section{\textcolor{teal}{Summary}}
  \resumeSubHeadingListStart
  \item []{System programmer with 14+ years of experience in Networking, OS, Cloud and Distributed systems}
  \resumeSubHeadingListEnd

%--------TECHNICAL SKILLS------------
\section{\textcolor{teal}{Technical Skills}}
\resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Go, C}
      \hfill
     \textbf{Technologies}{: Linux, TCP/IP, Docker, DPDK, OVS,  Electron}
   }
    \resumeSubHeadingListEnd
    
%-----------EXPERIENCE-----------------
\section{\textcolor{teal}{Experience}}
  \resumeSubHeadingListStart

       \resumeSubheading
      {Nuage Networks From Nokia}{\textcolor{teal}{Bengaluru, KA}}
      {Senior Technical Specialist}{\textcolor{GRAY}{Jan 2020 - Present}}
      \resumeItemListStart
        \resumeItem{Nuage VNS}
          {
           Nuage Networks Virtualized Network Services (VNS) delivers SD-WAN 2.0 functionality that allows seamless connection accross branch offices and data centers. I am part of the data-plane team and am instrumental in developing features/applications like
           \begin{itemize}
           \item {Forward Error Correction over overlay networks}
           \item {Implementation of passthrough for Trustsec packets over overlay and underlay}
           \item {Containerization of Nuage Services Gateway(CPE) to run on public clouds}
           \item {Exploring new technologies like XDP to replace OVS-DPDK}
           \end{itemize}}
      \resumeItemListEnd
    \resumeSubheading
      {Ionos Networks Inc./IPCore Solutions Pvt. Ltd}{\textcolor{teal}{Bengaluru, KA}}
      {Cloud Dataplane Lead}{\textcolor{GRAY}{Nov 2014 - Dec 2019}}
      \resumeItemListStart
        \resumeItem{Quantum File Transfer(QFX)}
          {
           QFX is a file/directory sync solution that can operate at Gigabit speeds over intercontinental distances. The software is built to scale to tens of  million files and tens of  terabytes of data. I was responsible for architecture of the data-plane and led a small team of engineers to develop software for
           
           \begin{itemize}
           \item {Multicast secure file/directory sync using high speed data transport over TCP/IP}
           \item {Dynamic path detection, healing and Congestion Control}
           \item {Network resource allocation, management, fault tolerance and resiliency}
           \item {Client apps on MacOS and Linux to replace CPEs}
           \item {Develop up a docker based upgrade mechanism to upgrade CPEs}
           \end{itemize}}
      \resumeItemListEnd
	  
    \resumeSubheading
      {CSR India Pvt. Ltd/Qualcomm India Pvt. Ltd.}{\textcolor{teal}{Bengaluru, KA}}
      {Senior Software Engineer}{\textcolor{GRAY}{Jan 2013 - Nov 2014}}
      \resumeItemListStart
        \resumeItem{Synergy WiFi Stack}
        {I was responsible for requirements analysis, design and development for mac802.11 based driver for an 802.11AC chip}
      \resumeItemListEnd

    \resumeSubheading
      {Sandvine India Pvt. Ltd.}{\textcolor{teal}{Bengaluru, KA}}
      {Sr. Engineer}{\textcolor{GRAY}{May 2012 - Dec 2012}}
      \resumeItemListStart
        \resumeItem{Sandvine’s Signaling Controller}
          {
          Modification and Enhancement of Linux Virtual Server (LVS) module to support SNAT and DNAT traffic.
          }
      \resumeItemListEnd

    \resumeSubheading
      {Brocade Communications India Pvt. Ltd.}{\textcolor{teal}{Bengaluru, KA}}
      {Software Engineer II}{\textcolor{GRAY}{Apr 2011 - May 2012}}
      \resumeItemListStart
        \resumeItem{Brocade’s Project Mercury}
      {Developed a dynamic Kernel Module Tracing Infrastructure to profile various kernel calls.}
		  \resumeItemListEnd
		
		 \resumeSubheading
      {Mindtree Ltd.}{\textcolor{teal}{Bengaluru, KA}}
      {Module Lead/Sr. Engineer/Engineer}{\textcolor{GRAY}{Jul 2007 - Apr 2011}}
      \resumeItemListStart
        \resumeItem{Embedded Software Practice}
      {
         \begin{itemize}
          \item{Design and Development of SIP based 2-way Video Conferencing feature on Android}
          \item{DRTL -- Implementation of a deadline aware scheduler, Deadline aware locking, and deadline aware interrupt handling in the Linux kernel}
          \item {Remotification of WiFi driver companion application and driver enhancements for a series of Wi-Fi chipsets}
          \item {Development of Linux device drivers for Touch screen controllers on Atmel AT91SAM9261/AT91RM9200 platform. (I2C, SPI, GPIO)}
		\end{itemize}
		}
\resumeItemListEnd
  \resumeSubHeadingListEnd
    
%--------TECHNICAL Interests------------
%\section{\textcolor{teal}{Technical Interests}}
%\resumeSubHeadingListStart
  %  \item{Operating Systems, Networking, Distributed Computing, Cloud Computing, Functional Programming}
  %  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{\textcolor{teal}{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Birla Institute of Technology and Science}{\textcolor{teal}{Bengaluru, KA}}
      {Master of Technology in Software Systems(Work Integrated Learning Program);  CGPA: 8.10}{\textcolor{GRAY}{Jul. 2017 -- Jul. 2019}}
    \resumeSubheading
      {Bengal Engineering and Science University, Shipbur (now IIEST, Shibpur)}{\textcolor{teal}{Howrah, West Bengal}}
      {Bachelor of Engineering in Information Technology;  81.2\% }{\textcolor{GRAY}{Aug. 2003 -- July. 2007}}
      \resumeSubheading
      {Holy Mission High School}{\textcolor{teal}{Samastipur, Bihar}}
      {CBSE - AISSCE(XII); 84\%}{\textcolor{GRAY}{2001}}
      \resumeSubheading
      {Central Public School}{\textcolor{teal}{Samastipur, Bihar}}
      {CBSE - AISSE(X); 85\%}{\textcolor{GRAY}{1999}}
  \resumeSubHeadingListEnd

%-----------Publications and Presentations-----------------
\section{\textcolor{teal}{Publications and Presentations}}
  \resumeSubHeadingListStart
    \item {“\textbf{Deployment Specific Real Time Linux}” on 23rd Sep, 2009 at the 1st LinuxCon in Portland, OR, USA}
    \item  {“\textbf{An Efficient Technique for Enhancing Forensic Capabilities of Ext2 file system}” at the 7th Annual Digital Forensic Research Workshop in Pittsburgh, PA, USA.}
  \resumeSubHeadingListEnd
  
  

%-----------Achievements/Rewards-----------------
\section{\textcolor{teal}{Achievements/Rewards}}
  \begin{enumerate}
    \item{Outstanding performer of the year 2008-09}
    \item{Half-yearly award 2008}
    \item{Topper in campus learning program conducted by MindTree Ltd}
    \item{School Topper in AISSCE-2001}
    \item{Awarded National Scholarship for getting All India Highest in Science in AISSE 1999}  
    \end{enumerate}


%-------------------------------------------
\end{document}
